
\documentclass[a4paper,11pt]{article}

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{enumitem}

%tabularx environment
\usepackage{tabularx}

\usepackage{fancyhdr}
\usepackage[english]{babel}

%----------FONT OPTIONS----------
%  sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header \& footer fields
\fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

\usepackage{geometry}
    \geometry{
    a4paper,
    lmargin=1cm, 
    rmargin=1cm,
    tmargin=0.5cm,
    bmargin=0.5cm
 }


%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{HTML}{0466c8}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
% \addbibresource{citations.bib}
% \setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
% \usepackage{showframe}


\begin{document}
\raggedright

% non-numbered pages
\pagestyle{empty} 

%% custom environments %%
\newcommand{\workheading}[4]{
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} @ \textit{#2} & \textit{#3} $|$ #4 \\
		\end{tabular*}\vspace{-7pt}
}

\newcommand{\projheading}[3]{
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} $|$ \textit{#2} & #3 \\
		\end{tabular*}\vspace{-7pt}
}

\newcommand{\eduheading}[4]{
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} (#2) & \textit{#3} $|$ #4 \\
		\end{tabular*}\vspace{-7pt}
}

\newcommand{\hack}[3]{
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} @ #2 & #3 \\
		\end{tabular*}\vspace{-1pt}
}

\newcommand{\award}[4]{
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} \textit{#4} & \textit{#2} $|$ #3 \\
		\end{tabular*}\vspace{-1pt}
}

\newcommand{\CVitem}[1]{
	\item[--]{
		{#1\vspace{-7pt}}
	}
}

\newcommand{\BeginCVItemList}{\begin{itemize}[topsep=0pt]}
\newcommand{\EndCVItemList}{\end{itemize}}

\newcommand{\spacebetweenitems}{\vspace{3pt}}
\newcommand{\spaceaftersectionheading}{\vspace{-7pt}}
\newcommand{\spaceaftersesctions}{\vspace{-5pt}}

\newenvironment{skill}[1]{\textbf{#1}: }{\vspace{-7pt}}
\newenvironment{work}[4]{\workheading{#1}{#2}{#3}{#4}}{}
\newenvironment{project}[3]{\projheading{#1}{#2}{#3}}{}
\newenvironment{school}[4]{\eduheading{#1}{#2}{#3}{#4}}{}
\newenvironment{extra}[3]{\projheading{#1}{#2}{#3}}{}

%% HEADER %%

\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Nathalie Redick} \\[3pt]
    \large{\textit{United States \& Canada}} \\[2pt]
    \href{tel:+15184104084}{\raisebox{-0.05\height}\faPhone \ +1 (518) 410 4084} \ $|$ \ 
    \href{mailto:nathalieredick@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nathalieredick@gmail.com} \ $|$ \ 
    \href{https://github.com/nredick}{\raisebox{-0.05\height}\faGithub\ nredick} \ $|$ \ 
    \href{https://linkedin.com/in/nredick}{\raisebox{-0.05\height}\faLinkedin\ nredick} 
    % \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \
\end{tabularx}

%% BODY %% 
\spaceaftersectionheading

\section{Education}
\spaceaftersectionheading
\school{McGill University}{3.71 / 4.00}{Montreal, QC}{Sep. 2019 -- May 2023}{
    \BeginCVItemList
    \CVitem{B.A. in \textbf{Computer Science} with a Minor in \textbf{Earth \& Planetary Sciences} \& a Supplementary Minor Concentration in Computer Science.}
    % \CVitem{\textit{Relevant Coursework}: Algorithms \& Data Structures, Data Science, Linear Algebra I \& II, Discrete Math, Probability, Statistics, Applied Machine Learning, Probabilistic Programming.}
    \EndCVItemList
}\spacebetweenitems

\spaceaftersesctions
\section{Skills}
\spaceaftersectionheading    \skill{Programming Languages}{\small Python, C++, C, Java, R, Julia, MATLAB, HTML/CSS, OCaml, MIPS Assembly.}\\
    \skill{Tools}{\small Git, Unix, \LaTeX, Jupyter, AWS EC2, VS Code, QGIS, ArcGIS Pro, Microsoft Office Suite, Windows, MacOS.}\\
    % \skill{Inter-personal Skills}{\small Effective communicator \& problem-solver who is adaptable, creative, \& motivated.}
\spaceaftersesctions

\section{Experience}
\spaceaftersectionheading
\work{Data Science Intern}{\href{https://www.esri.com/en-us/home}{Esri}}{Remote}{May 2022 -- Aug. 2022}{ 
    \BeginCVItemList
    \CVitem{Implemented an automated workflow for updating national hydrography datasets using Esri's Multi-Task Road Extractor \textbf{deep learning} model.}
    \CVitem{Improved the baseline ML model by designing new input image layers \& geomorphological indicators.}
    \CVitem{Improved the baseline model by ~4\% accuracy to \textbf{96.3\% accuracy and 0.85 MIOU} by designing new input image layers \& geomorphological indicators.}
    \EndCVItemList
}\spacebetweenitems

% \work{Project Manager}{RedQuoin}{Wilton, NY}{May 2021 -- Aug. 2021}{ 
%     \BeginCVItemList 
%     \CVitem{Facilitated communication between the software engineer, business consultant, \& the head of the start-up.}
%     \CVitem{Conceptualized the design of the software's UI/UX \& visual identity to improve user experience.}
%     \EndCVItemList
% }\spacebetweenitems

% \work{Undergraduate Research Assistant}{\href{https://www.eps.mcgill.ca/~crowe/EQprocesses}{EQP Research Group}}{McGill University}{Jan. 2021 -- Aug. 2021}{ 
%     \BeginCVItemList 
%     \CVitem{Indiviudally designed \& built a website using \textbf{HTML/CSS \& some JS} for communicating seismological data of Qu\'ebec to promote public awareness about local earthquake hazards.}
%     \EndCVItemList
% }\spacebetweenitems

\work{Software Development Consultant}{\href{https://redbuddevelopment.com}{Redbud Development}}{Wilton, NY}{Jan. 2020 -- May 2021}{ 
    \BeginCVItemList 
    \CVitem{Designed \& built a macOS desktop app in Python that is used to process project budget data for clients.}
    \CVitem{Implementing the app into the workflow \textbf{reduced proposal creation time by 95\%.}}
    \EndCVItemList
}\spacebetweenitems

\work{Software Engineering Intern}{\href{http://bluespiral.io}{Blue Spiral Interactive}}{Saratoga Springs, NY}{May 2019 -- Aug. 2019}{ 
    \BeginCVItemList 
    \CVitem{Strengthened in-house marketing analysis software by working with a team to build a \textbf{RESTful API} for accessing \& visualising marketing data.}
    \CVitem{Individually developed a pipeline in Python to standardise 10GB of NYS voter registration data to map on QGIS; map was designed to advise a spatially-informed political campaign strategy.}
    \CVitem{\textbf{Taught} myself Python, Git, \& QGIS over the course of the internship. I also gained experience with parallel computing, \textbf{reducing execution time by 97\%}.}
    \EndCVItemList
}\spacebetweenitems

% \work{Software Development Intern}{\href{https://garnetriver.com}{Garnet River}}{Saratoga Springs, NY}{Feb. 2019 -- Jun. 2019}{ 
%     \BeginCVItemList 
%     \CVitem{Evaluated the efficacy \& usability of computer vision products from Microsoft, Google, \& AWS.}
%     \EndCVItemList
% \spacebetweenitems

\spaceaftersesctions

\section{Projects}
\spaceaftersectionheading

\project{U-Net Tool For Geospatial Analysis}{Interdisciplinary Research}{Sep. 2022 -- Present}{
    \BeginCVItemList
    \CVitem{Collaborating with \href{https://scholar.google.ca/citations?user=Q3Hc-jEAAAAJ&hl=en}{Dr. Matthew Tarling} to implement a \textbf{U-Net image segmentation model} that can be used by researchers to analyze geospatial problems.}
    \CVitem{Our objective is to create a tool that can be used by anyone, regardless of their technical background.}
    \EndCVItemList
}\spacebetweenitems

\project{\href{https://tensorboard.dev/experiment/1Wfk0uKbT0OTM34i7SzliA}{Using Machine Learning to Identify Landslides}}{Interdisciplinary Research}{May 2021 -- Present}{
    \BeginCVItemList
    \CVitem{Independently designed a research project to implement an image segmentation ML model to identify landslides using new geological and physical indicators.}
    \CVitem{Collaborating with the CGS to implement new methods into the landslide identification workflow \& to improve the performance of the model.}
    \CVitem{Current interation of the model boasts \textbf{95.3\% accuracy \& a loss of 0.19.}}
    \EndCVItemList
}\spacebetweenitems

\spaceaftersesctions

\section{Extra-curriculars}
\spaceaftersectionheading
\extra{Member}{\href{https://mcgillai.com}{McGill Artificial Intelligence Society}}{Sep. 2022 -- Present}{
    \BeginCVItemList
    \CVitem{Participated in monthly discussions on AI, attended workshops, \& participated in other events.}
    \EndCVItemList
}\spacebetweenitems

\extra{Vice President Communications}{\href{https://www.monteregiansociety.com}{The Monteregian Society} at McGill University}{Sep. 2020 -- Present}{
    \BeginCVItemList
    \CVitem{Managed communications for the undergraduate student council for Earth \& Planetary Sciences.}
    \CVitem{Designed \& built the council's website to host student resources, events, \& other information.}
    \EndCVItemList
}\spacebetweenitems

% National Honor Society (2017 – 2019)
\spaceaftersesctions

% \section{Professional Development}
% \spaceaftersesctions

\section{Awards}
\spaceaftersectionheading
\BeginCVItemList
\CVitem{Awardrd both \textbf{Best Design} \& \textbf{Most Fun \& Creative} hack, leading a team of 3 to design a COVID-19 spoof of \href{https://pacdemic-man-2vsjz.ondigitalocean.app}{Pac-Man WebGL game} using Unity Game Engine, competing against 332 participants at \href{https://devpost.com/software/mcha-ck-fee-antivirus-2022-pan-demic-man}{McHacks9}.}
\CVitem{Won \textbf{Best AI Hack for Art} against 111 participants at MAIS Hacks 2021 for \href{https://devpost.com/software/maispeare}{MAISpeare}, a LSTM-driven web app that generates a poem from any image.}
\CVitem{Awarded \textbf{Best Overall Hack} in my first hackathon at MAIS Hacks 2020 by leading a team against 115 participants to create a XGBoost-driven web app that predicts a user's MBTI Personality Type based on their Tweet data.}
\EndCVItemList

% \hack{Most Useless Hack}{\href{https://devpost.com/software/read-between-the-wines}{MAIS Hacks 2022}}{Oct. 2022}
% \hack{Best Design \& Most Creative}{\href{https://devpost.com/software/mcha-ck-fee-antivirus-2022-pan-demic-man}{McHacks9}}{Jan. 2022}
% \hack{Best AI Hack for Art}{\href{https://devpost.com/software/maispeare}{MAIS Hacks 2021}}{Oct. 2021}
% \hack{Best Overall Hack}{\href{https://devpost.com/software/mbti-personality-classifier-2eho6w}{MAIS Hacks 2020}}{Oct. 2020}
\award{\href{https://www.geotop.ca/en/formation/bourses/bourses-geotop}{Geotop 2021 Scholarship Competition}}{Geotop}{2021}{(\$1500)}
\award{Alma Mater Scholarship}{McGill University}{2019}{(\$3000)}
\award{Stat Staff Professionals Computer Science Scholarship}{Saratoga Springs High School}{2019}{(\$1000)}
% \award{\href{https://apstudents.collegeboard.org/awards-recognitions/ap-scholar-award}{National AP Scholar}}{College Board}{2019}{}
% \award{\href{https://apstudents.collegeboard.org/awards-recognitions/ap-scholar-award}{AP Scholar with Distinction}}{College Board}{2018, 2019}{}
% Academic High Honor Roll (2015 – 2019)
% cany scholarship from dean 
\spaceaftersesctions

% hackathon wins 
% research scholarship (jamie, geotop)
% alma mater scholarship
% cs award in high school 


% \spaceaftersesctions

% \section{Publications}
% \spaceaftersesctions


%% FOOTER %% 
\vfill
\center{\footnotesize Last updated: \today}
\end{document}
